Applying Deep Learning to Acoustic Analysis in the PICO-60 Dark Matter Detector

### 2018-08-07 documentation/paper.tex
Added performance table

One of the main purposes of semi-supervised learning is to handle the impure training data effectively, and learn to replicate the imperfectly represented underlying pattern (nuclear recoils versus alpha particles) rather than merely fitting to separate run types.

Therefore, performance is quantified by how accurately a system is able to replicate Acoustic Parameter, rather than simply reproduce the labels provided. Accuracy of the neural network in the original PICO-60 paper is also provided as a baseline.

@@

>>>>

One of the main purposes of semi-supervised learning is to handle the impure training data effectively, and learn to replicate the imperfectly represented underlying pattern (nuclear recoils versus alpha particles) rather than merely fitting to separate run types. Therefore, performance is quantified by how accurately a system is able to replicate Acoustic Parameter, rather than simply reproduce the labels provided.

@@

\subsection{Performance Summary}

The following table directly compares performance of the semi-supervised learning systems, and also includes the neural network used in the original PICO-60 paper as a baseline.

\begin{tabular}{|l|l|l|l|}
    Technique & Max Accuracy & Max Mean by Run & $dim(\varsigma)=128$ Errors versus 256 \\
    Gravitational Differentiation & 98\% & 96\% & 64\% Increase \\
    Iterative Cluster Nucleation & 100\% & 98\% & 85\% Increase \\
    Original PICO-60 NN & X\% & N/A & N/A
\end{tabular}
